---
title: "R Notebook"
output: html_notebook
---


```{r}
pacman::p_load(tidyverse, haven, magrittr, highcharter)
```

```{r}
crimestats <- readxl::read_excel("table-21a.xls")

options(scipen = 999)
```


```{r}
crimestats %<>% 
  mutate(offenders = `Black or
African
American`) %>% 
  mutate(offense = `Offense charged`) %>% 
  mutate(totalblack = 43320651) %>% 
  mutate(perc_black = offenders / totalblack) %>% 
  mutate(nonoffenders = 43320651 - offenders) %>% 
  select(offense, offenders, totalblack, perc_black, nonoffenders)
crimestats$`Offense charged`


#install.packages("waffle")
#
#
#crimestats %>% 
#  filter(offense == "TOTAL") %>% 
#  select(totalblack, nonoffenders) %>% 
#waffle::waffle()
```

# highcharter stuff

```{r}
mpgman3 <- mpg %>% 
  group_by(manufacturer) %>% 
  summarise(n = n(), unique = length(unique(model))) %>% 
  arrange(-n, -unique) %>% 
  glimpse()
## Observations: 15
## Variables: 3
## $ manufacturer <chr> "dodge", "toyota", "volkswagen", "ford", "chevrol...
## $ n            <int> 37, 34, 27, 25, 19, 18, 14, 14, 13, 9, 8, 5, 4, 4, 3
## $ unique       <int> 4, 6, 4, 4, 4, 3, 2, 2, 3, 1, 1, 1, 1, 1, 1
mpgman3
hchart(mpgman3, "treemap", hcaes(x = manufacturer, value = n, color = unique))


`%notin%` <- Negate(`%in%`)
crimestats %>% 
  filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4")) %>% 
  select(offense, offenders) %>% 
#  mutate(id = 1:n()) %>% 
  gather(-offense, key = "id", value = "offenders") %>%
  mutate(unique = 0) %>% 
  select(-id) %>% 
  rbind(data.frame(offense = "nonoffenders", offenders = 43320651, unique = 0.1)) %>% 
hchart("treemap", hcaes(x = offense, value = offenders, color = unique)) %>% hc_add_theme(hc_theme_smpl())

hctreemap2()

plot_dat <- crimestats %>% 
  filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4"))

plot_dat2 <- plot_dat %>% 
  select(offense, offenders) %>% 
#  mutate(id = 1:n()) %>% 
  gather(-offense, key = "id", value = "offenders") %>%
  mutate(unique = 0) %>% 
  select(-id) %>% 
  left_join(plot_dat %>% select(offense, perc_black), by = "offense") %>% 
  rbind(data.frame(offense = "Non-Offenders", 
                   offenders = 43320651, 
                   unique = 0.1, 
                   perc_black = 1 - sum(plot_dat$perc_black))) %>%
    filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4")) 

  hctreemap2(data = plot_dat2,
    group_vars = "offense",
    size_var = "offenders", 
    color_var = "unique",
    annotations = "perc_black",
    layoutAlgorithm = "squarified",
    levelIsConstant = FALSE,
    levels = list(
      list(level = 1, dataLabels = list(enabled = TRUE)),
      list(level = 2, dataLabels = list(enabled = T)),
      list(level = 3, dataLabels = list(enabled = FALSE))
    )
  ) %>% 
  highcharter::hc_legend(enabled = F) %>%
  hc_colorAxis(minColor = RColorBrewer::brewer.pal(7, "Blues")[7],
               maxColor = RColorBrewer::brewer.pal(7, "Blues")[5]) %>% 
  hc_add_series(data = ds, type = "treemap") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Individuals: {point.value:,.0f}") #%>%
#  hc_tooltip(formatter = JS("function(){
#                            return ('Individuals: ' + this.perc_black)
#                            }")
#  )
  

  
  
highcharter::list_parse(plot_dat2)  %>% 
hchart("treemap", hcaes(x = offense, value = offenders, color = unique)) %>% hc_add_theme(hc_theme_smpl())


```


```{r}
library(viridisLite)
library(dplyr)

colorvar <- mtcars$hp
cols <- viridis(1000)[round(ecdf(colorvar)(colorvar)*1000)]
cols <- substr(cols, 0, 7)

dt <- mtcars %>% 
  mutate(x = wt, y = mpg, z = drat, color =  cols)

ds <- highcharter::list_parse(dt)

hc2 <- highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_series(data = ds, type = "bubble") %>%
  hc_tooltip(formatter = JS("function(){
                            return ('y: ' + this.y + ' <br> Number of gears: ' + this.point.gear)
                            }")
  )

hc2
```


```{r}
library(treemap)
library(viridisLite)

data(GNI2014)

tm <- treemap(plot_dat2, index = c("offense"),
              vSize = "offenders", vColor = "unique",
              type = "value", palette = viridis(6))


ds <- highcharter::list_parse(plot_dat2)

highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_series(data = ds, type = "tree", x = offense, value = offenders, color = unique) %>%
#hchart(hcaes()) %>% 
  hc_tooltip(formatter = JS("function(){
                            return ('y: ' + this.y + ' <br> Number of gears: ' + this.point.gear)
                            }"))

highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_series(data = ds, type = "bubble") %>%
  hc_tooltip(formatter = JS("function(){
                            return ('y: ' + this.y + ' <br> Number of gears: ' + this.point.gear)
                            }")
  )

hctreemap(tm)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
