---
title: "Crime Rates by Race"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---


Treemaps based on [FBI Crime Data 2016](https://ucr.fbi.gov/crime-in-the-u.s/2016/crime-in-the-u.s.-2016/topic-pages/tables/table-21) and [United States Census Bureau Data 2016](https://www.census.gov/quickfacts/fact/table/US/AGE135216)


```{r, echo=FALSE, warning=F,message=FALSE}
pacman::p_load(tidyverse, haven, magrittr, highcharter)
```

```{r, echo=FALSE, warning=F,message=FALSE}
crimestats <- readxl::read_excel("table-21a.xls")

options(scipen = 999)
```

# Black People

**Total Black Population in the USA is 429.759.60 (2016)**

```{r, echo=FALSE, warning=F,message=FALSE}
crimestats_black <- crimestats %>% 
  mutate(offenders = `Black or
African
American`) %>% 
  mutate(offense = `Offense charged`) %>% 
  mutate(totalblack = 42975960) %>% 
  mutate(perc_black = offenders / totalblack) %>% 
  mutate(nonoffenders = 42975960 - offenders) %>% 
  select(offense, offenders, totalblack, perc_black, nonoffenders)

```

Assuming each arrest is one unique person (highly unlikely, some individuals get arrested more often) $5.27\%$ (*2.263.112* individuals) of the black population were arrested for some offense. If we only take violent crime[^1] into account $0.35\%$ (*153.341* individuals) of the black population were arrested for violent offenses.


```{r, echo=FALSE}
`%notin%` <- Negate(`%in%`)

viol_crime <- c("Murder and nonnegligent manslaughter", "Rape3", "Robbery", "Aggravated assault")

prop_crime <- c("Burglary", "Larceny-theft", "Motor vehicle theft", 
"Arson")

plot_dat <- crimestats_black %>% 
  filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4"))

plot_dat2 <- plot_dat %>% 
  select(offense, offenders) %>% 
#  mutate(id = 1:n()) %>% 
  gather(-offense, key = "id", value = "offenders") %>%
  mutate(unique = case_when(
    offense %in% viol_crime ~ 0,
    offense %in% prop_crime ~ 0.5,
    TRUE ~ 0.7
  )) %>% 
  select(-id) %>% 
  left_join(plot_dat %>% select(offense, perc_black), by = "offense") %>% 
  rbind(data.frame(offense = "Non-Offenders", 
                   offenders = 42975960, 
                   unique = 1, 
                   perc_black = 1 - sum(plot_dat$perc_black))) %>%
    filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4")) 

  hctreemap2(data = plot_dat2,
    group_vars = "offense",
    size_var = "offenders", 
    color_var = "unique",
    annotations = "perc_black",
    layoutAlgorithm = "squarified",
    levelIsConstant = FALSE,
    levels = list(
      list(level = 1, dataLabels = list(enabled = TRUE)),
      list(level = 2, dataLabels = list(enabled = T)),
      list(level = 3, dataLabels = list(enabled = FALSE))
    )
  ) %>% 
  highcharter::hc_legend(enabled = F) %>%
  hc_colorAxis(minColor = "red",
               maxColor = "lightgrey") %>% 
#  hc_colors(c("#111FDB", "#0FD63E", "#ED34DE", "#575757")) %>% 
#  hc_add_series(data = ds, type = "treemap") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Individuals: {point.value:,.0f}") %>%   
  hc_add_theme(hc_theme_smpl()) #%>%
#  hc_tooltip(formatter = JS("function(){
#                            return ('Individuals: ' + this.perc_black)
#                            }")
#  )
  
  

```

# White People
**Total White Population in the USA is 248.485.057 (2016)**

```{r, echo=FALSE}
crimestats_white <- crimestats %>% 
  mutate(offenders = White) %>% 
  mutate(offense = `Offense charged`) %>% 
  mutate(totalwhite = 248485057) %>% 
  mutate(perc_white = offenders / totalwhite) %>% 
  mutate(nonoffenders = 248485057 - offenders) %>% 
  select(offense, offenders, totalwhite, perc_white, nonoffenders)

```



```{r, echo=FALSE}
`%notin%` <- Negate(`%in%`)

viol_crime <- c("Murder and nonnegligent manslaughter", "Rape3", "Robbery", "Aggravated assault")

prop_crime <- c("Burglary", "Larceny-theft", "Motor vehicle theft", 
"Arson")

plot_dat <- crimestats_white %>% 
  filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4"))

plot_dat2 <- plot_dat %>% 
  select(offense, offenders) %>% 
#  mutate(id = 1:n()) %>% 
  gather(-offense, key = "id", value = "offenders") %>%
  mutate(unique = case_when(
    offense %in% viol_crime ~ 0,
    offense %in% prop_crime ~ 0.5,
    TRUE ~ 0.7
  )) %>% 
  select(-id) %>% 
  left_join(plot_dat %>% select(offense, perc_white), by = "offense") %>% 
  rbind(data.frame(offense = "Non-Offenders", 
                   offenders = 248485057, 
                   unique = 1, 
                   perc_white = 1 - sum(plot_dat$perc_white))) %>%
    filter(offense %notin% c("TOTAL", "Violent crime4", "Property crime4")) 

  hctreemap2(data = plot_dat2,
    group_vars = "offense",
    size_var = "offenders", 
    color_var = "unique",
    annotations = "perc_white",
    layoutAlgorithm = "squarified",
    levelIsConstant = FALSE,
    levels = list(
      list(level = 1, dataLabels = list(enabled = TRUE)),
      list(level = 2, dataLabels = list(enabled = T)),
      list(level = 3, dataLabels = list(enabled = FALSE))
    )
  ) %>% 
  highcharter::hc_legend(enabled = F) %>%
  hc_colorAxis(minColor = "red",
               maxColor = "lightgrey") %>% 
#  hc_colors(c("#111FDB", "#0FD63E", "#ED34DE", "#575757")) %>% 
#  hc_add_series(data = ds, type = "treemap") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
             Individuals: {point.value:,.0f}") %>%   
  hc_add_theme(hc_theme_smpl()) #%>%
#  hc_tooltip(formatter = JS("function(){
#                            return ('Individuals: ' + this.perc_white)
#                            }")
#  )
  
  

```


Assuming each arrest is one unique person (highly unlikely, some individuals get arrested more often) $2.36\%$ (*5.858.330* individuals) of the white population were arrested for some offense. If we only take violent crime into account $0.09\%$ (*241.063* individuals) of the white population were arrested for violent offenses. 

[^1]: FBI Definition of violent crime: "Violent crimes are offenses of murder and nonnegligent manslaughter, rape, robbery, and aggravated assault."